Moment Constraints Make Learning Latent-Variable Models Easier

### 2014-01-31 doc/icml2014/directed.tex
Updated figures and some details and notation

To address the first, we will need that the following assumption on the
  parameters of the model:
\begin{assumption} 
  \label{asm:full-rank-plus}
  For every clique $\sC = \{h_{i_1}, \cdots, h_{i_m}\} \in \sG$, let
    $Z_\sC$ be the marginal distribution for that clique. 
  Then every mode-$i$ unfolding of $Z_\sC$ has full column rank.
\end{assumption}
Intuitively, the assumption guarantees that the marginal probability of
  any hidden state is non-zero.

@@

\begin{lemma}(Canonical form) 
  \label{lem:reduction}
  Every directed graphical model can be transformed into one in which
  the observed variables are leaves with exactly one parent.
\end{lemma}
\begin{proof}
  \begin{figure}
    \label{fig:reduction}
    \centering
    \subimport{figures/}{reduction.tikz}
    \caption{Reduction to canonical form.}
  \end{figure}

  Let $x$ be an observed variable with parents $h_1, \cdots, h_p$ and
  children $h_{p+1}, \cdots, h_c$. Replace $x$ with a phantom hidden
  variable $h_x$, and make $x$ the child of $h_x$ (\figureref{reduction}). The domain of $h_x$
  has the same as $x$, and $\mOpp{x}{h_x} = I$.

  The parameters for $h_x$ are the same as $x$.
\end{proof}

>>>>

To address the first, we will need that the following assumption on the
  parameters of the model:
\begin{assumption} 
  \label{asm:full-rank-plus}
  For every clique $\sC = \{h_{i_1}, \cdots, h_{i_m}\} \in \sG$, let
    $Z_\sC$ be the marginal distribution for that clique. 
  Then every mode-$i$ unfolding of $Z_\sC$ has full column rank.\verify
\end{assumption}
Intuitively, the assumption guarantees that the marginal probability of
  any hidden state is non-zero.

@@

\begin{lemma}(Canonical form) 
  \label{lem:reduction}
Every directed graphical model can be transformed into one in which
  the observed variables are leaves with exactly one parent. 
There is a one-to-one correspondence between the parameters of this
  transformed model and the original one.
\end{lemma}
\begin{proof}
  \begin{figure}
    \label{fig:reduction}
    \centering
    \subimport{figures/}{reduction.tikz}
    \caption{Reduction to canonical form.}
  \end{figure}

  \providecommand{\hp}{\ensuremath{h_{\textrm phantom}}}

  Let $x_v$ be an observed variable with parents $P$ and children $C$.
  Consider the following transformation.
  Replace $x_v$ with a phantom hidden variable \hp with the same
  parents $P$ and children $C \union \{x_{v_1}, x_{v_2}, x_{v_3}\}$,
  where $x_{v_1},x_{v_2},x_{v_3}$ are three copies of $x$
  (\figureref{reduction}).

  The domain of $\hp$ is the same as $x$
    \footnote{Though we have assumed that all hidden variables share the
      same domain, $[k]$, our work generalizes to hidden domains of
      arbitrary sizes, provided \assumptionref{full-rank-plus} holds.}
    and $\mOpp{v}{\textrm{phantom}} = I$.

  Then, for any clique $\sC \contains \hp$, the parameters in the
    original graphical model can be obtained by substituting $\hp$ with
    $x_v$.
\end{proof}

### 2014-01-31 doc/icml2014/intro.tex
Updated figures and some details and notation

\begin{figure}[t]
  \label{fig:approach}
  \centering
\begin{tikzpicture}

% Import grid.
%\node[scale=0.9] (step0) at (0,0) {\input{figures/grid.tikz}};
\node[scale=0.9] (step1) at (0cm,0cm) {\input{figures/grid-outline.tikz}};
\node[scale=0.75, below=0.5 cm of step1.south] { \textbf{Step 1:} Identify bottlenecks};
\node[scale=0.9] (step2) at (5cm,0cm) {\input{figures/factors.tikz}};
\node[scale=0.75, below=0.5 cm of step2.south] { \textbf{Step 2:} Optimize piecewise likelihoods};

\draw[-latex] (step1) -- (step2);

\end{tikzpicture}
  \caption{Overview of approach}
\end{figure}

>>>>

\begin{figure}[t]
  \label{fig:approach}
  \centering
  \subimport{figures/}{approach.tikz}
  \caption{Overview of approach}
\end{figure}
